Sampling requirements to detect ecosystem change

### 2020-03-05 R/manuscript_draft.Rmd
edit the style of facet_wrap title so they match base r and figures look more homogeneous

p1 <- 
ggplot(simulation_all %>% filter(Parameter == unique(simulation_all$Parameter)[1]), aes(Param, min_time)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept=ar_vr$acf[2], lty=2) + 
  facet_wrap(~Parameter, scales="free_x", 
             labeller = label_glue('(a) {Parameter}')) +
  ylim(20,50) +
  labs(x=c("sigma"), y= "Minimum number of samples required") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

p2 <- ggplot(simulation_all %>% filter(Parameter == unique(simulation_all$Parameter)[2]), aes(Param, min_time)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = sd_vr, lty=2) +
  facet_wrap(~Parameter, scales="free_x", 
             labeller = label_glue('(b) {Parameter}')) +
  ylim(20,50) +
  labs(x="phi", y= "") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
p3 <- ggplot(simulation_all %>% filter(Parameter == unique(simulation_all$Parameter)[3]), aes(Param, min_time))  +
  geom_point() +
  geom_line() + 
  geom_vline(xintercept = shift_vr, lty=2) +
  facet_wrap(~Parameter, scales="free_x", 
             labeller = label_glue('(c) {Parameter}')) +
  ylim(20,50) +
  labs(x="shift size", y= "") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

@@

p1  <- ggplot(myoutput_summary, aes(x=number_samples,y=mean_distance)) + geom_line()  + geom_ribbon(aes(ymin = mean_distance - 1.96*sd_distance, ymax = mean_distance + 1.96*sd_distance), fill = "grey80") +geom_line(size=1) + coord_cartesian(ylim = c(2.2, 50))  + 
  facet_wrap(~approach,
             labeller = label_glue('({.l}) {approach} sampling ')) + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  labs(x="Total number of samples analyzed", y="Distance to real changepoint") #+
 # theme(legend.position = c(0.93, 0.72),
#       legend.background = element_rect(fill = "#ffffffaa", colour = NA),
#        legend.title=element_text(size=7), 
 #       legend.text=element_text(size=8)) +
#  guides(pch=guide_legend(title="Initial number\nof sample"))

@@

# Plot
p1 <- if(several_n2_init) {
  ggplot(myoutput[myoutput$target_cpt==1,], aes(final_n,diff_real, pch=factor(n2_init))) + 
  geom_hline(aes(yintercept=0), col=adjustcolor("black", alpha.f = .4)) + 
  geom_point(alpha = .3) +
  facet_wrap(~method,
             labeller = label_glue('({.l}) {method} sampling ')) + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  labs(x="Total number of samples analyzed", y="Distance to real changepoint") +
  theme(legend.position = c(0.93, 0.72),
        legend.background = element_rect(fill = "#ffffffaa", colour = NA),
        legend.title=element_text(size=7), 
        legend.text=element_text(size=8)) +
  guides(pch=guide_legend(title="Initial number\nof sample"))
} else {
  ggplot(myoutput[myoutput$target_cpt==1 & myoutput$n2_init == 5,], aes(final_n,diff_real)) + 
  geom_hline(aes(yintercept=0), col=adjustcolor("black", alpha.f = .4)) + 
  geom_point(alpha = .3) +
  facet_wrap(~method,
             labeller = label_glue('({.l}) {method} sampling ')) + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  labs(x="Total number of samples analyzed", y="Distance to real changepoint") 
}

>>>>

p1 <- 
ggplot(simulation_all %>% filter(Parameter == unique(simulation_all$Parameter)[1]), aes(Param, min_time)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept=ar_vr$acf[2], lty=2) + 
  facet_wrap(~Parameter, scales="free_x", 
             labeller = label_glue('a. {Parameter}')) +
  ylim(20,50) +
  labs(x=c("phi"), y= "Minimum number of samples required") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        strip.background = element_rect(colour="transparent", fill="transparent"),
        strip.text.x = element_text(angle = 0, hjust = 0))
p2 <- ggplot(simulation_all %>% filter(Parameter == unique(simulation_all$Parameter)[2]), aes(Param, min_time)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = sd_vr, lty=2) +
  facet_wrap(~Parameter, scales="free_x", 
             labeller = label_glue('b. {Parameter}')) +
  ylim(20,50) +
  labs(x="phi", y= "") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        strip.background = element_rect(colour="transparent", fill="transparent"),
        strip.text.x = element_text(angle = 0, hjust = 0))
p3 <- ggplot(simulation_all %>% filter(Parameter == unique(simulation_all$Parameter)[3]), aes(Param, min_time))  +
  geom_point() +
  geom_line() + 
  geom_vline(xintercept = shift_vr, lty=2) +
  facet_wrap(~Parameter, scales="free_x", 
             labeller = label_glue('c. {Parameter}')) +
  ylim(20,50) +
  labs(x="shift size", y= "") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        strip.background = element_rect(colour="transparent", fill="transparent"),
        strip.text.x = element_text(angle = 0, hjust = 0))

@@

p1  <- ggplot(myoutput_summary, aes(x=number_samples,y=mean_distance)) + geom_line()  + geom_ribbon(aes(ymin = mean_distance - 1.96*sd_distance, ymax = mean_distance + 1.96*sd_distance), fill = "grey80") +geom_line(size=1) + coord_cartesian(ylim = c(2.2, 50))  + 
  facet_wrap(~approach,
             labeller = label_glue('{.l}. {approach} sampling ')) + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        strip.background = element_rect(colour="transparent", fill="transparent"),
        strip.text.x = element_text(angle = 0, hjust = 0)) +
  labs(x="Total number of samples analyzed", y="Distance to real changepoint") #+
 # theme(legend.position = c(0.93, 0.72),
#       legend.background = element_rect(fill = "#ffffffaa", colour = NA),
#        legend.title=element_text(size=7), 
 #       legend.text=element_text(size=8)) +
#  guides(pch=guide_legend(title="Initial number\nof sample"))

@@

# Plot
p1 <- if(several_n2_init) {
  ggplot(myoutput[myoutput$target_cpt==1,], aes(final_n,diff_real, pch=factor(n2_init))) + 
  geom_hline(aes(yintercept=0), col=adjustcolor("black", alpha.f = .4)) + 
  geom_point(alpha = .3) +
  facet_wrap(~method,
             labeller = label_glue('{.l}. {method} sampling ')) + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        strip.background = element_rect(colour="transparent", fill="transparent"),
        strip.text.x = element_text(angle = 0, hjust = 0)) +
  labs(x="Total number of samples analyzed", y="Distance to real changepoint") +
  theme(legend.position = c(0.93, 0.72),
        legend.background = element_rect(fill = "#ffffffaa", colour = NA),
        legend.title=element_text(size=7), 
        legend.text=element_text(size=8)) +
  guides(pch=guide_legend(title="Initial number\nof sample"))
} else {
  ggplot(myoutput[myoutput$target_cpt==1 & myoutput$n2_init == 5,], aes(final_n,diff_real)) + 
  geom_hline(aes(yintercept=0), col=adjustcolor("black", alpha.f = .4)) + 
  geom_point(alpha = .3) +
  facet_wrap(~method,
             labeller = label_glue('{.l}. {method} sampling ')) + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        strip.background = element_rect(colour="transparent", fill="transparent"),
        strip.text.x = element_text(angle = 0, hjust = 0)) +
  labs(x="Total number of samples analyzed", y="Distance to real changepoint") 
}
